Computer Science House Constitution

### 2025-10-06 constitution.tex
correct voting member expectations

\titleclass{\subsubsubsection}{straight}[\subsection]

\newcounter{subsubsubsection}[subsubsection]
\renewcommand\thesubsubsubsection{\thesubsubsection.\arabic{subsubsubsection}}
\renewcommand\theparagraph{\thesubsubsubsection.\arabic{paragraph}} % optional; useful if paragraphs are to be numbered

\titleformat{\subsubsubsection}
  {\normalfont\normalsize\bfseries}{\thesubsubsubsection}{1em}{}
\titlespacing*{\subsubsubsection}
{0pt}{3.25ex plus 1ex minus .2ex}{1.5ex plus .2ex}

\makeatletter
\renewcommand\paragraph{\@startsection{paragraph}{5}{\z@}%
  {3.25ex \@plus1ex \@minus.2ex}%
  {-1em}%
  {\normalfont\normalsize\bfseries}}
\renewcommand\subparagraph{\@startsection{subparagraph}{6}{\parindent}%
  {3.25ex \@plus1ex \@minus .2ex}%
  {-1em}%
  {\normalfont\normalsize\bfseries}}
\def\toclevel@subsubsubsection{4}
\def\toclevel@paragraph{5}
%\def\toclevel@paragraph{6}
\def\toclevel@subparagraph{6}
\def\l@subsubsubsection{\@dottedtocline{4}{7em}{4em}}
\def\l@paragraph{\@dottedtocline{5}{10em}{5em}}
\def\l@subparagraph{\@dottedtocline{6}{14em}{6em}}
\makeatother

\setcounter{secnumdepth}{7}
\setcounter{tocdepth}{7}

@@

\begin{document}

% Title
\maketitle

@@

The following requirements must be met for an Active Member to be allowed to vote after the first Intro Evals of the academic year.
Any of these requirements may be waived by the Evals Director or an E-Board Vote.
\begin{enumerate}
	\item Attend at least six House Meetings
	\item Attend at least six directorship meetings
	\item Attend at least one CSH social event
	\item Attend at least two Technical Seminars
\end{enumerate}

>>>>

@@

\begin{document}
% Title
\maketitle

@@

The following requirements must be met for an Active Member to be allowed to vote after the first Intro Evals of the academic year.
Any of these requirements may be waived by the Evals Director or an E-Board Vote.
\begin{enumerate}
	\item Attend all House Meetings
	\item Attend at least six directorship meetings
	\item Attend at least one CSH social event
	\item Attend at least two Technical Seminars
\end{enumerate}
